### 2020-07-01 evaluation.tex
后两部分

\section{Evaluation and Case Study}
\label{sec-evaluation}
% \begin{figure*}[!t]
%     \centering
%     \subfigure[Traditional Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_1.pdf}\label{fig-control-1}}
%     \subfigure[Optical Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_1_2.pdf}\label{fig-control-2}}
%     \subfigure[Traditional Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_2.pdf}\label{fig-random-1}}
%     \subfigure[Optical Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_2_2.pdf}\label{fig-random-2}}
%     \hfill
%     \caption{Performance in Controlled Environment (a,b) and Random Environment (c,d).}
%     \label{fig-performance-1}
% \end{figure*}
We evaluate the performance of the network model in different training and testing conditions. We perform the following experiments with two COTS smartphones: a Redmi 6A smartphone, with a single rear camera with 13 million pixels and digital zoom only, and a HUAWEI P40 Pro, with multiple rear cameras. The telephoto camera possesss up to 5x optical zooming ability which we will utilize fully in our experiments.

\subsection{Performance In Controlled Environments}
In these experiments, we train and test the model with the images captured with exactly the same environment parameters, and used Peak Signal to Noise Ratio to evaluate the accuracy of the recovered images. The results are shown in Figure~\ref{fig-control-1} and Figure~\ref{fig-control-2}. Moreover, the ultimate goal of our system is the readability of the recovered images, so we also used Optical Character Recognition(OCR) services to evaluate the accuracy. The model with traditional lenses (without optical zoom) is trained and tested at 1-2 meters range, while the one with optical zoom at 5-7.5 meters, at which distance less than 5\% of the characters (only the simplest ones) can be recognized by humans from the photos without the assistance of SR algorithms.

From Figure~\ref{fig-control-1}, we can see the model can achieve an OCR accuracy above 90\% at 1.8m with traditional lenses in both day and night time. The PSNR is higher than 10 as well. The OCR accuracy and PSNR drops in night time since the darker environmental lighting condition as well as with the increasing of distance since the longer distance means more blurs. For Figure~\ref{fig-control-2}, we can see the OCR accuracy is larger than 90\% at 6m with optical zooming lenses. The performance is relatively consistent in both day and night time. Considering the complexity of Chinese characters, and the assist of context when read by an OCR recognizer, we believe this level of accuracy can provide sufficient data at a shoulder surfing scenario, thus proving the efficiency of our model.
\begin{figure}[!t]
    \centering
    \subfigure[Traditional Lens]{\includegraphics[width=0.36\textwidth]{./pic/data_1.pdf}\label{fig-control-1}}
    \subfigure[Optical Lens]{\includegraphics[width=0.36\textwidth]{./pic/data_1_2.pdf}\label{fig-control-2}}
    \hfill
    \caption{Performance in Controlled Environment using Traditional Lens and Optical Lens.}
    \label{fig:control}
\end{figure}

@@

\subsection{Performance In Random Environments}
We train the model with data captured in different environments, as mentioned before, and test its ability in other environments. The results are shown in Figure~\ref{fig-random-1} and Figure~\ref{fig-random-2}. For Figure~\ref{fig-random-1}, the model can still achieve an OCR accuracy above 85\% at 1.8m with traditional lenses. From Figure~\ref{fig-random-2}, the OCR accuracy keeps higher than 90\% at 6m with optical zooming lenses. This verifies the efficiency of our model for environment adaption.

@@

\subsection{Adapting Ability}
We train the model with fewer groups of data, exposing it to fewer variations of environment parameters, and examine the model's performance in other environments. The results are shown in Figure~\ref{fig-adapt-tranditional}.

@@

\subsection{Comparison with other architectures}
We train and test other commonly used architectures with the same sets of data and evaluate their results. We chose SRCNN, a commonly used single image SR network, and applied it to each single image before merging the results by pixel-level average. We also used a multi-frame version of CNN consisting of 3D convolutional layers, designed for video super resolution(VideoSR). However, as mentioned above, it is very difficult for the single image approaches to utilize information and distinguish the noisy and deformed patterns, while VideoSR approaches rely upon consistency between frames, so they fail to give satisfactory results. We used the relatively easy 'daytime 1.2m-distance direct with traditional lenses' group of data for testing. The results are shown in Table~\ref{table-comp}.
\begin{table}[!t]
    \centering
    \caption{Comparison with existing systems.}
    \begin{tabular}{@{}cccc@{}}
        \toprule
    System & SRPeek & SRCNN & VideoSR \\ \midrule
    PSNR(db) & 13.32 & 7.69 & 8.403\\ 
    OCR Accuracy(\%) & 100 & 10 & 23\\ \bottomrule
    \end{tabular}
    \label{table-comp}
\end{table}

@@

% \section{System Evaluation}
\subsection{Accuracy}
We build the system on smartphone and evaluate its performance in real-life environments. We experiment with a Redmi 6A smartphone (with a camera of 13 million pixels) for the attacker and a HUAWEI Mate8 smartphone for the victim. As the telephoto cameras can assist the attacker to see clearly at approximately 3m distance without any aid from SR algorithms, we believe it is insignificant to further extend this distance to judge it as a threat to privacy, so that the following experiments are performed with traditional lenses at 1-2m range. We ask 5 human participants to read the reconstructed characters to evaluate the usability of our model. No participants can read the unprocessed images, but all of them can decipher the information on the reconstructed image without much difficulty. The results are shown in Table~\ref{table-scenarios}.

@@

\begin{table}[!t] 
    \centering
    \caption{Impact of hand tremors while holding various items.}
    \begin{tabular}{ccccc}
        \toprule
    Items & None & Camera & Target & Both  \\
    \midrule
    Baseline & 5 & 0 & 5& 5\\ 
    \midrule
    OCR & 95 & 85 & 80 & 80\\ 
    Human & 95 & 85 & 80 & 85\\ \bottomrule
    \end{tabular}
    \label{table-tremor}
\end{table}

@@

\begin{figure}[!t]
    \centering
    \subfigure[Traditional Lens]{\includegraphics[width=0.36\textwidth]{./pic/data_5.pdf}\label{fig-image-tranditional-2}}
    \subfigure[Optical Lens]{\includegraphics[width=0.36\textwidth]{./pic/data_6.pdf}\label{fig-image-optical-2}}
    \hfill
    \caption{Performance with various processing images using Traditional Lens and Optical Lens.}
    \label{fig:adapting}
\end{figure}

\subsection{Success rate in different tasks}
We test the success rate of obtaining crucial information when the observed participant perform several tasks on a phone: reading text message, typing text message, entering PIN, and typing password with numbers, English and special characters. The observed participant will turn off the screen of his phone as soon as he/she finishes the task, while the observing participant will observe through our APP, constantly capturing images and processing them to display a real-time and magnified view of the observed phone. For the first two tasks, we ask the observing participant several questions to test if he/she have collected the vital information(e.g. the name or the location mentioned in the text). For the task of recognizing PIN and passwords, we use accuracy per character as a supplementary evaluation metric. In these two scenarios, we ignore the virtual keyboard and view only the textbox, assuming that the last character of the entered string is always visible. Less photos will be available for each character but decipfering English characters is also easier than Chinese characters, and we trained a model specifically for each task(with the same neural network architecture), the training images containing only English characters and numbers(or only numbers for the PIN entry scenario). The results are shown in Table~\ref{table-task}.

\begin{table}[!t]
\centering
\begin{tabular}{@{}ccccc@{}}
	\toprule
Accuracy & Read text & Type text & Enter PIN & Enter password\\ \midrule
Raw Image & 5 & 0 & 0 & 0\\
SRPeek & 100 & 100 & 100 & 80\\ \bottomrule
\end{tabular}
\caption{Success rate in different tasks.}
\label{table-task}
\end{table}

@@

\subsection{Perceived shoulder surfing susceptibility}
We ask the observed participant to rate the perceived shoulder-surfing susceptibility in these scenario. The attacker will be sitting or standing behind the participant at 1.5m range, pretending to be interacting with their own phone while continuously running the shoulder-surfing APP. None of the participants were alerted by the attacker's behavior and reported suspicion of shoulder-surfing. We believe that our system can enable a malicious attacker to gather large amounts of critical information from the victim while remaining unnoticed.

>>>>

\section{Model Evaluation}
\label{sec-evaluation}
% \begin{figure*}[!t]
%     \centering
%     \subfigure[Traditional Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_1.pdf}\label{fig-control-1}}
%     \subfigure[Optical Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_1_2.pdf}\label{fig-control-2}}
%     \subfigure[Traditional Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_2.pdf}\label{fig-random-1}}
%     \subfigure[Optical Lens]{\includegraphics[width=0.24\textwidth]{./pic/data_2_2.pdf}\label{fig-random-2}}
%     \hfill
%     \caption{Performance in Controlled Environment (a,b) and Random Environment (c,d).}
%     \label{fig-performance-1}
% \end{figure*}
We evaluate the performance of the network model in different training and testing conditions. We perform the following experiments with two COTS smartphones: a Redmi 6A smartphone, with a single rear camera with 13 million pixels and digital zoom only, and a HUAWEI P40 Pro, with multiple rear cameras. The telephoto camera possesss up to 5x optical zooming ability which we will utilize fully in our experiments.

\subsection{Performance In Controlled Environments}
In these experiments, we train and test the model with the images captured with exactly the same environment parameters, and used Peak Signal to Noise Ratio to evaluate the accuracy of the recovered images. The results are shown in Figure~\ref{fig-control-1} and Figure~\ref{fig-control-2}. Moreover, the ultimate goal of our system is the readability of the recovered images, so we also used Optical Character Recognition(OCR) services to evaluate the accuracy. The model with traditional lens without optical zoom(hereafter refered as traditional lens) is trained and tested at 1-2 meters range, while the lens with optical zoom(hereafter refered as optical lens) at 5-7.5 meters, at which distance less than 5\% of the characters (only the simplest ones) can be recognized by humans from the photos without the assistance of SR algorithms. The PSNR and OCR results are shown in Fig. ~\ref{fig-control-1}.

This model can achieve an OCR accuracy above 90\% at 1.8m with traditional lens in both day and night time. The PSNR is higher than 10 as well. OCR accuracy and PSNR drops in night time since the darker environmental lighting condition as well as with the increasing of distance since the longer distance means more blurs. For Figure~\ref{fig-control-2}, we can see the OCR accuracy is larger than 90\% at 6m with optical lens. The performance is relatively consistent in both day and night time. Considering the complexity of Chinese characters, and the assist of context when read by an OCR recognizer, we believe this level of accuracy can provide sufficient data at a shoulder surfing scenario, thus proving the efficiency of our model.
\begin{figure}[!t]
    \centering
    \subfigure[Traditional Lens]{\includegraphics[width=0.36\textwidth]{./pic/data_1.pdf}\label{fig-control-1}}
    \subfigure[Optical Lens]{\includegraphics[width=0.36\textwidth]{./pic/data_1_2.pdf}\label{fig-control-2}}
    \hfill
    \caption{Performance in Controlled Environment using Traditional Lens and Optical Lens.}
    \label{fig:control}
\end{figure}

@@

\subsection{Performance In Random Environments}
We train the model with data captured in different environments, as mentioned before, and test its ability in other environments. The results are shown in Figure~\ref{fig-random-1} and Figure~\ref{fig-random-2}. For Figure~\ref{fig-random-1}, the model can still achieve an OCR accuracy above 85\% at 1.8m with traditional lens. From Figure~\ref{fig-random-2}, the OCR accuracy keeps higher than 90\% at 6m with optical lens. This verifies the efficiency of our model for environment adaption.

@@

\subsection{Performance with fewer avaliable images}
\begin{figure}[!t]
    \centering
    \subfigure[Traditional Lens]{\includegraphics[width=0.36\textwidth]{./pic/data_5.pdf}\label{fig-image-tranditional-2}}
    \subfigure[Optical Lens]{\includegraphics[width=0.36\textwidth]{./pic/data_6.pdf}\label{fig-image-optical-2}}
    \hfill
    \caption{Performance with fewer avaliable images using Traditional Lens and Optical Lens.}
    \label{fig:number}
\end{figure}
As mentioned in sec.~\ref{sec-design}, our model is designed to work on any number of input images, the only limitation being that these images are snapshots of the same scene. This design is requisite because in certain scenraios the data displayed on the victim's screen is transient and ever-changing, e.g. password entry, where only the last character of the password is visible. We evaluated the impact of fewer avaliable images to the performance of the SR model. The results are shown in fig.~\ref{fig:number}. We tested at the 1.8m daytime scenario for traditional lens and 6m daytime scenario for optical lens.

In the tradition lens group the performance of the model drops dramatically with fewer than 10 images, indicating that not enough input information is avaliable to rule out all possibilities of the displayed characters. The optical lens group displayed a steady decent of accuracy when fewer images are avaliable, which is expected, as the blur patterns are more complex and the differences between frames more pronounced, so that the images are more precious to the model and contain less overlapping data, and removing any of them will cause losses in accuracy.

\subsection{Adapting Ability}
We train the model with fewer groups of data, exposing it to fewer variations of environment parameters, and examine the model's performance in other environments. The results are shown in Figure~\ref{fig:adapting}.

@@

\subsection{Comparison with other architectures}
We train and test other commonly used architectures with the same sets of data and evaluate their results. We chose SRCNN, a commonly used single image SR network, and applied it to each single image before merging the results by pixel-level average. We also used a multi-frame version of CNN consisting of 3D convolutional layers, designed for video super resolution(VideoSR). However, as mentioned above, it is very difficult for the single image approaches to utilize information and distinguish the noisy and deformed patterns, while VideoSR approaches rely upon consistency between frames, so they fail to give satisfactory results. We used the relatively easy 'daytime 1.2m-distance direct with traditional lens' group of data for testing. The results are shown in Table~\ref{table-comp}.
\begin{table}[!t]
    \centering
    \caption{Comparison with existing systems.}
    \begin{tabular}{@{}cccc@{}}
        \toprule
    System & SRPeek & SRCNN & VideoSR \\ \midrule
    PSNR(db) & 13.32 & 7.69 & 8.403\\ 
    OCR Accuracy(\%) & 100 & 10 & 23\\ \bottomrule
    \end{tabular}
    \label{table-comp}
\end{table}

@@

% \section{System Evaluation}
\section{Case Study}
\subsection{Accuracy}
We build the system on smartphone and evaluate its performance in real-life environments. We experiment with a Redmi 6A smartphone (with a camera of 13 million pixels) for the attacker and a HUAWEI Mate8 smartphone for the victim. As the telephoto cameras can assist the attacker to see clearly at approximately 3m distance without any aid from SR algorithms, we believe it is insignificant to further extend this distance to judge it as a threat to privacy, so that the following experiments are performed with traditional lens at 1-2m range. We ask 5 human participants to read the reconstructed characters to evaluate the usability of our model. No participants can read the unprocessed images, but all of them can decipher the information on the reconstructed image without much difficulty. The results are shown in Table~\ref{table-scenarios}.

@@

\begin{table}[!t] 
    \centering
    \caption{Impact of hand tremors when the camera(attacker phone) and/or target(victim phone) is handheld.}
    \begin{tabular}{ccccc}
        \toprule
    Items & None & Camera & Target & Both  \\
    \midrule
    Baseline & 5 & 0 & 5& 5\\ 
    \midrule
    OCR & 95 & 85 & 80 & 80\\ 
    Human & 95 & 85 & 80 & 85\\ \bottomrule
    \end{tabular}
    \label{table-tremor}
\end{table}

@@

\subsection{Success rate in different tasks}
We test the success rate of obtaining crucial information when the observed participant perform several tasks on a phone: reading text message, typing text message, entering PIN, and typing password with numbers, English and special characters. The observed participant will turn off the screen of his phone as soon as he/she finishes the task, while the observing participant will observe through our APP, constantly capturing images and processing them to display a real-time and magnified view of the observed phone. For the first two tasks, we ask the observing participant several questions to test if he/she have collected the vital information(e.g. the name or the location mentioned in the text). For the task of recognizing PIN and passwords, we use accuracy per character as a supplementary evaluation metric. In these two scenarios, we ignore the virtual keyboard and view only the textbox, assuming that the last character of the entered string is always visible. Fewer photos will be available for each character but decipfering English characters is also easier than Chinese characters, and we trained a model specifically for each task(with the same neural network architecture), the training images containing only English characters and numbers(or only numbers for the PIN entry scenario). The results are shown in Table~\ref{table-task}.

\begin{table}[!t]
\centering
\caption{Success rate in different tasks.}
\label{table-task}
\begin{tabular}{@{}ccccc@{}}
	\toprule
Accuracy & Read text & Type text & Enter PIN & Enter password\\ \midrule
Raw Image & 5 & 0 & 0 & 0\\
SRPeek & 100 & 100 & 100 & 80\\ \bottomrule
\end{tabular}

\end{table}

@@

\subsection{Perceived shoulder surfing susceptibility}
We ask the observed participant to rate the perceived shoulder-surfing susceptibility in these scenario. The attacker will be sitting or standing behind the participant at 1.8m range, pretending to be interacting with their own phone while continuously running the shoulder-surfing APP. None of the participants were alerted by the attacker's behavior and reported suspicion of shoulder-surfing. We believe that our system can enable a malicious attacker to gather large amounts of critical information from the victim while remaining unnoticed.

### 2020-07-01 implementation.tex
fig
后两部分

As the experiment goes on, the attacker phone will keep on taking photos in burst mode (20 photos per time), and the victim phone will change the characters it is displaying at a fixed interval, when approximately 100 images were taken by the attacker. We change the environmental setting whenever about 2k photos were taken, relocating the phones (while keeping their distance between 1 and 2 meters) or modifying the angle of the phones. The attacker will always point its phone directly at the victim, keeping its screen in the middle of the photos; The victim, however, may tilt its phone at an angle within 30 degrees. We then readjust the focus and aperture of the attacker's phone to maximize the image quality before continuing data collection. Screenshots were taken in the victim's phone each time it changes its display, and these screenshots are scaled, spun and deformed according to the distance and angle between the phones at the time, and used as ground truth for training and evaluation.

@@

\subsection{Training Process}
Because of the difficulties in discovering the patterns among the blurry images, the training process is not so straightforward and somewhat time-consuming. Our approach is as follows: we first collect 60,000 images at a stationary experiment setting and train the model with it, as mentioned in Sec~\ref{sec-experiment-setting}, until we get satisfactory results on the test dataset. The model should be able to handle this task easily. After that, we use transfer learning methods to fine tune the model in order to fit different environmental parameters. We add a small percentage of image data from another similar experiment setting into the training data and resume training. When the model stabilizes, continue adding data from the same setting until the model can equally process data from the two image collections. Note that in this process the model will tend to extract false features, displaying wrong but clear texts as result. This phenomenon can be mitigated with dropout and normalization layers. As the model successfully fits two of the image sets, we repeat this procedure for several times until it shows signs of self-adapting, for example, when presented photos taken at 2.0m and 1.5m range in the training process, the model fits 1.75m photos easily. After that, the model can learn with the full fully-shuffled dataset with fewer difficulties.

>>>>

As the experiment goes on, the attacker phone will keep on taking photos in burst mode (20 photos per time), and the victim phone will change the characters it is displaying at a fixed interval, when approximately 100 images were taken by the attacker. We change the environmental setting whenever about 2k photos were taken, relocating the phones (while keeping their distance between 1 and 2 meters) or modifying the angle of the phones. The attacker will always point its phone directly at the victim, keeping its screen in the middle of the photos; The victim, however, may tilt its phone at an angle within 30 degrees. We then readjust the focus and aperture of the attacker's phone to maximize the image quality before continuing data collection. Screenshots were taken in the victim's phone each time it changes its display, and these screenshots are scaled, spun and deformed according to the distance and angle between the phones at the time, and used as ground truth for training and evaluation.
\begin{figure}
	\centering
	\includegraphics[width=0.48\textwidth]{pic/setup.pdf}
    \caption{Illustration of our experimental setting (Distance between phones are shortened for demonstration).}
	\label{illustration_of_system}
\end{figure}
% \begin{figure}
%   \centering
%      \centering
%      \subfigure[Experiment setting. Distance between phones are shortened for demonstration.]{
%          \includegraphics[width=0.5\textwidth]{pic/exp1.jpg}
%          \label{fig-exp1}
%          }
%    \subfigure[screenshot from attacker's phone(SRPeek system).]{
%          \includegraphics[width=0.5\textwidth]{pic/exp2.jpg}
%          \label{fig-exp2}
%          }
%    \subfigure[screenshot from victim's phone.]{
%          \includegraphics[width=0.5\textwidth]{pic/exp3.jpg}
%          \label{fig-exp3}
%          }
%      \caption{Illustration of our experimental setting.}
%      \label{fig-experiment}
% \end{figure}

@@

\subsection{Training Process}
Because of the difficulties in discovering the patterns among the blurry images, the training process is not so straightforward and somewhat time-consuming. Our approach is as follows: we first collect 60,000 images at a stationary experiment setting and train the model with it, as mentioned in Sec~\ref{sec-experiment-setting}, until we get satisfactory results on the test dataset. The model should be able to handle this task easily. After that, we use transfer learning methods to fine tune the model in order to fit different environmental parameters. We add a small percentage of image data from another similar experiment setting into the training data and resume training. When the model stabilizes, continue adding data from the same setting until the model can equally process data from the two image collections. Note that in this process the model will tend to extract false features, displaying wrong but clear texts as result. This phenomenon can be mitigated with dropout and normalization layers. As the model successfully fits two of the image sets, we repeat this procedure for several times until it shows signs of self-adapting, for example, when presented photos taken at 1.8m and 1.2m range in the training process, the model fits 1.5m photos easily. After that, the model can learn with the full fully-shuffled dataset with fewer difficulties.
